Last glacial cycle glacier erosion potential in the Alps

### 2021-01-29 articles/erosion/alps-erosion.tex
Rework the conclusions. Call it 0.5 second draft.

    \note{I still need to develop the conclusions.}

    The modelled erosion rates are very highly uncertain. The results are
    limited as there is no feedback of erosion onto ice dynamics, and
    erosion by rivers is not included. But if a square-law is used:
    \begin{itemize}
      \item Cumulative erosion potential is strongly localized in regions
        of fast past glacier flow.
      \item The total erosion rate is not correlated with the ice volume.
      \item During major glaciations, erosion rates are high at low elevation,
        but the mountain's interior is preserved.
      \item Higher-elevation glacial erosional landforms were formed during
        stages of intermediate glaciation.
      \item Erosion increases during deglaciations, regardless of surface
        meltwater availability.
    \end{itemize}

>>>>

    Due to stacked-up uncertainties regarding paleoclimate, glacier sliding and
    erosion processes, our quantitative results are to be considered with extreme
    uncertainties. Yet to the best of our current knowledge in these respective
    areas of science, we can draw the following qualitative conclusions:
    \begin{itemize}
      \item The non-linear physics of glacier deformation and sliding, combined
        with non-linear empirical erosion laws, results in a very strong
        localization of rapid glacier erosion in regions of fast flow.
      \item Temperature-dependent creep and basal sliding provide a mechanism
        for accelerated erosion during deglaciation periods, irrespective of
        surface meltwater penetration to the glacier bed.
      \item If a non-linear glacier erosion law is used, the climate-induced
        slowdown of erosion counterbalances glacier expansion, so that
        Alpine-wide glacier erosion rates do not correlate with the ice volume.
      \item Rapid glacier erosion is restricted to low elevation during stages
        of glacier advance and maximum glaciation, but propagates up-valley to
        higher elevations during periods of glacier retreat.
      \item The diversity of the Alpine glacial erosion landscape appears to
        be the time-transgressive signature of a variety of glacial stages
        ranging from pan-Alpine ice sheets to modern-style mountain glaciers.
    \end{itemize}
